% Adapted from http://www.latextemplates.com/template/wilson-resume-cv

\documentclass[11pt]{article}
\usepackage[top=1in, right=1in, left=1in, bottom=1in]{geometry}
\usepackage{fancyhdr, lastpage, enumitem, titlesec, scrextend}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{changepage}
\usepackage{pdfpages}
\usepackage{tikz}
\usetikzlibrary{calc}

\usepackage[none]{hyphenat}
\raggedright

\newcommand{\myname}{Daniel (Dan) J. Kats}
\newcommand{\myemail}{dkats@mgh.harvard.edu}
\newcommand{\myemailhref}{\href{mailto:\myemail}{\myemail}}
\newcommand{\myphone}{(617) 584-2485}

\fancypagestyle{myfirststyle}{
	\fancyhf{}
	\fancyfoot[L]{\textit{\today}}
	\fancyfoot[C]{}
	\fancyfoot[R]{\textit{Page \thepage\ of \pageref*{LastPage}}}
	\renewcommand{\headrulewidth}{0pt}
	\renewcommand{\footrulewidth}{0.1pt}
}
\fancypagestyle{mypagestyle}{
	\fancyhf{}
	\fancyhead[L]{\myname}
	\fancyhead[R]{\myemailhref\ \sqbullet\ \ \myphone}
	\fancyfoot[L]{\textit{\today}}
	\fancyfoot[C]{}
	\fancyfoot[R]{\textit{Page \thepage\ of \pageref*{LastPage}}}
	\renewcommand{\headrulewidth}{0.1pt}
	\renewcommand{\footrulewidth}{0.1pt}
}
\pagestyle{mypagestyle}
\thispagestyle{myfirststyle}

\newcommand{\mysec}[1]{\subsection*{\uppercase{#1}}}
\titleformat{\subsection}{\normalsize\bfseries}{\thesubsection}{1em}{}
\titlespacing{\subsection}{0pt}{6pt}{*0}	% {section}{left}{before}{after}
\setlength\parindent{0pt}
\setlength\parskip{6pt}
\setlist[itemize]{nosep,itemsep=0pt,before=\vspace{3pt},after=\vspace{3pt}}

\newcommand{\bibsec}[1]{\underline{\normalsize\bfseries#1}}
\newcommand{\bibssec}[1]{{\normalsize\bfseries#1}}

\definecolor{darkblue}{HTML}{000063}
\hypersetup{
	colorlinks=true,
	linkcolor=darkblue,
	urlcolor=darkblue,
}

% Size of indent of sections
\newcommand{\blockindent}{0.25in}

% Custom square bullet point definition
\newcommand{\sqbullet}{~\vrule height 1ex width .8ex depth -.2ex}
\def\labelitemi{\sqbullet}
\def\labelitemiii{$\diamond$}

\renewcommand{\title}[1]{
{\huge{\textbf{#1}}}\\
}

\newcommand{\school}[4]{
\textbf{#1}, {#2} \\
{#3} \hfill {#4}\\
}

\newcommand{\job}[4]{
\textbf{#1}, {#2} \\
{#3} \hfill {#4}\\
}

\newcommand{\jobtitle}[2]{
{#1} \hfill {#2}\\
}

%------------------------------------------------

\begin{document}

\parbox{0.5\textwidth}{
	\vspace*{-0.5cm}
	\title{\myname}
}
\hfill
{\fontsize{10pt}{11.5pt}\selectfont
	\parbox{0.3\textwidth}{
		\vspace*{-1.0cm}
		\begin{tabbing}
		\hspace{3cm}	\= \hspace{4cm} \= \kill % Spacing within the block
		{\bf Email}	\` \myemailhref \\
		{\bf Phone}	\` \myphone \\
		{\bf Address} 	\` 28 Grove St.\\
						\` Apt. 6\\
						\` Boston, MA 02114\\
		\end{tabbing}
		\vspace*{-8mm}
	}
}
\rule{\textwidth}{0.5mm}

%------------------------------------------------

\vspace{-0.5mm}
\mysec{Education}
\begin{adjustwidth}{\blockindent}{0cm}
\school{\href{http://www.brandeis.edu/}{\textbf{Brandeis University}}}{Waltham, MA}{Bachelor of Science in Biochemistry}{May 2016}
\begin{itemize}

	\item Summa cum laude with high honors, GPA 3.85

	\item Thesis: ``\href{http://hdl.handle.net/10192/32359}{Inosine 5'-monophosphate dehydrogenase: A collection of mysterious binding sites and regulation}''

\end{itemize}

\school{\href{http://www.case.edu/}{\textbf{Case Western Reserve University}}}{Cleveland, OH}{Doctor of Medicine}{May 2020}
\begin{itemize}

	\item With Honors and Distinction in Research

	\item Thesis: ``Lung cancer risk stratification, Down syndrome, and epileptic spasms: A journey through informatics, healthcare disparities, and quality improvement''

\end{itemize}

\end{adjustwidth}

%------------------------------------------------

\vspace{-0.5mm}
\mysec{Postdoctoral Training}
\begin{adjustwidth}{\blockindent}{0cm}

\school{\href{https://www.massgeneral.org/children}{\textbf{Massachusetts General Hospital \textit{for} Children}}}{Boston, MA}{Resident Physician, Pediatrics}{June 2020 -- June 2023}

\end{adjustwidth}

%------------------------------------------------

\vspace{1pt}
\mysec{Honors and Awards}
% \begin{adjustwidth}{\blockindent}{0cm}

\begin{itemize}

	\vspace{-6pt}
	\item MassGeneral Hospital \textit{for} Children Teaching Award, PGY-1 \hfill June 2021

	\vspace{3pt}
	\item American Thoracic Society Abstract Scholarship \hfill May 2019\\
	(see \textsc{bibliography} \#\ref{ats19oral}, \ref{ats19poster}, \ref{ats19adie}, \ref{ats19tlimat})

	\vspace{3pt}
	\item Phi Beta Kappa honor society \hfill May 2016

	\vspace{3pt}
	\item NIH Computational Neuroscience Training Fellowship {\footnotesize(R90DA033463)} \hfill May 2014 -- May 2016

\end{itemize}

% \end{adjustwidth}

%------------------------------------------------

\vspace{1pt}
\mysec{Teaching}
\begin{adjustwidth}{\blockindent}{0cm}

\job{Case Western Reserve University School of Medicine}{Cleveland, OH}{Pediatric Clerkship}{March -- April 2020}
\begin{itemize}
	\item Re-organized the third year core clerkship curriculum into an online format to be compatible with the COVID-19 pandemic
	\item Designed a ``Mock Wards Day,'' in which students pre-rounded on a panel of virtual patients, presented, and dealt with simulated emergent clinical situations
\end{itemize}

\end{adjustwidth}

%------------------------------------------------

\mysec{Research Experience}
\begin{adjustwidth}{\blockindent}{0cm}

\job{\href{https://www.amoxclavdosing.com/}{Amoxicillin-clavulanate Dosing Calculator}}{MassGeneral Hospital, Boston, MA}{Co-Principal Investigator (Co-PI: Iman Moawad, PharmD, BCPPS)}{May 2021 -- Present}
\begin{itemize}

	\item Created a dosing calculator to assist clinicians in prescribing amoxicillin-clavulanate by ensuring proper dosing of both component drugs

\end{itemize}

\newpage
\job{\href{https://www.massgeneral.org/children/services/treatmentprograms.aspx?id=1701}{Down Syndrome Program}}{Massachusetts General Hospital \textit{for} Children, Boston, MA}{Co-Investigator (PI: Brian Skotko, MD, MPP)}{June 2020 -- Present}
\jobtitle{Research Assistant (PI: Brian Skotko, MD, MPP)}{October 2018 -- June 2020}
\begin{itemize}

	\item Project: World map of quality of life for people with Down syndrome
	\begin{itemize}
		\vspace{-3pt}
		\item Co-led a group of international Down syndrome experts to create the first worldwide quality of life survey for people with Down syndrome (that could be adapted to all groups of developmental/intellectual disabilities)
	\end{itemize}

	\vspace{3pt}
	\item Project: Literature review of infantile spasms in Down syndrome
	\begin{itemize}
		\vspace{-3pt}
		\item Publication: see \textsc{bibliography} \#\ref{katsroche20}
	\end{itemize}

	\vspace{3pt}
	\item Project: Interviews with parents of children with Down syndrome and infantile spasms
	\begin{itemize}
		\vspace{-3pt}
		\item Publication: see \textsc{bibliography} \#\ref{kats20}
	\end{itemize}

\end{itemize}

\job{Clinical Informatics}{The MetroHealth System, Cleveland, OH}{Researcher (PI: Yasir Tarabichi, MD, MSCR)}{May 2017 -- July 2019}
\begin{itemize}

	\item Project: The effects of smoking history variability in electronic health records (EHRs) on the ordering of lung cancer screening tests
	\begin{itemize}
		\vspace{-3pt}
		\item Publications: see \textsc{bibliography} \#\ref{katstarabichi20}, \ref{adie20}, \ref{tarabichi17}
		\item Presentations: see \textsc{bibliography} \#\ref{ats19oral}, \ref{lepow17}, \ref{ats20tlimat}, \ref{ats19poster}, \ref{ats19adie}, \ref{ats19tlimat}, \ref{ats18}
	\end{itemize}

	\item Project: Determining the optimal duration of benzodiazepine treatment for alcohol withdrawal to avoid benzodiazepine-related delirium

\end{itemize}

\job{\href{http://www.bio.brandeis.edu/hedstromlab/Site/Home.html}{Hedstrom Laboratory}}{Brandeis University, Waltham, MA}{Undergraduate Researcher (PI: Lizbeth Hedstrom, PhD)}{September 2013 -- May 2016}
\jobtitle{Computational Neuroscience Fellow}{May 2014 -- May 2016}
\begin{itemize}

	\item Project: Determining the significance of interactions among inosine 5'-monophosphate dehydrogenase (IMPDH), RNA polymerase, and ribsomes in \textit{Escherichia coli}

	\vspace{3pt}
	\item Designed and implemented method of \textit{in situ} chromosomal mutations without using biomarkers or scars (in collaboration with \href{http://www.bio.brandeis.edu/lovettlab/lovettlabhomepage.html}{Lovett Laboratory})

	% \vspace{3pt}
	\item Designed and wrote Python scripts to analyze IC$_{50}$ data of hundreds of inhibitors used with IMPDH from different organisms
	\begin{itemize}

		\vspace{-3pt}
		\item Goal: Find quick, easy, and cheap way to functionally categorize previously unused strains of IMPDH by using a small set of inhibitors

		\item Developed method to reduce entire set of inhibitors to a small representative subset

		\item Found drug outliers

		\item Visualized data to find patterns, drugs/enzymes of interest

	\end{itemize}

\end{itemize}

\end{adjustwidth}

%------------------------------------------------

\mysec{Bibliography}
\begin{adjustwidth}{\blockindent}{0cm}

\bibsec{Peer-Reviewed}
	\begin{enumerate}

		\item\label{katstarabichi20} \href{https://doi.org/10.1093/ntr/ntaa192}{\textbf{Kats, D.J.}, Adie, Y., Tlimat, A., Greco, P.J., Kaelber, D.C., Tarabichi, Y.. Assessing Different Approaches to Leveraging Historical Smoking Exposure Data to Better Select Lung Cancer Screening Candidates: A Retrospective Validation Study. \textit{Nicotine Tob Res}. 2020.}

		\item\label{katsroche20} \href{http://dx.doi.org/10.1002/epi4.12412}{\textbf{Kats, D.J.}, Roche, K.J., Skotko, B.G. Epileptic Spasms in Individuals with Down Syndrome: A Review of the Current Literature. \textit{Epilepsia Open}. 2020, 5: 344--353.}

		\item\label{kats20} \href{https://doi.org/10.1177/0883073820932770}{\textbf{Kats, D.J.}, Patsiogiannis, V., Skotko, B.G. Epileptic Spasms in Patients with Down Syndrome: Experiences from Caregivers. \textit{J Child Neurol}. 2020, 35(12): 813--819.}

		\item\label{adie20} \href{https://journal.chestnet.org/article/S0012-3692(19)34402-2/fulltext}{Adie, Y., \textbf{Kats, D.J.}, Tlimat, A., Perzynski, A., Dalton, J., Gunzler, D., Tarabichi, Y. Neighborhood Disadvantage and Lung Cancer Incidence in Ever-Smokers at a Safety-Net Healthcare System: A Retrospective Study. \textit{CHEST}. 2020, 157(4): 1021--1029.}

		\item\label{tarabichi17} \href{http://journal.chestnet.org/article/S0012-3692(17)33076-3/fulltext}{Tarabichi, Y., \textbf{Kats, D.J.}, Kaelber, D.C., Thornton, J.D. The Impact of Fluctuations in Pack-Year Smoking History in the Electronic Health Record on Lung Cancer Screening Practices. \textit{CHEST}. 2018, 153(2): 575--578.}

	\end{enumerate}

\bibsec{Lectures/Workshops}
	\begin{enumerate}[resume]

		\item\label{binca-hpv}[Local] \textbf{Kats, D.J.} Human Papillomavirus. Boston International Newcomers Academy. Boston, MA. May 2021.

		\item\label{journalclub21b}[Hospital] \textbf{Kats, D.J.}, Miozzo, P., Kung, E. Hospitalist Journal Club. Massachusetts General Hospital \textit{for} Children. Boston, MA. May 2021.

		\item\label{journalclub21a}[Hospital] \textbf{Kats, D.J.}, Miozzo, P., Schwartz, K., Kao, A. Hospitalist Journal Club. Massachusetts General Hospital \textit{for} Children. Boston, MA. April 2021.

		\item\label{cos21}[Hospital] \textbf{Kats, D.J.}, Zanger, K., Vakharia, J., Misra, M. Chief of Service: 14 year old with growth restriction and pituitary mass. Massachusetts General Hospital \textit{for} Children. Boston, MA. 2021.

		\item\label{amaace18}[National] \textbf{Kats, D.J.}, Mieso, B., Singh, M., Gullett, H., Koopman Gonzalez, S. Patient Navigation: Pre-Clinical Medical Students Experiencing Longitudinal Patient Relationships. Accelerating Change in Medical Education Consortium\\Student-Led Conference on Health Systems Science; Hershey, PA. 2018.

	\end{enumerate}

\bibsec{Oral Presentations}
	\begin{enumerate}[resume]

		\item\label{ats19oral}[International] \href{https://www.dankats.com/research/ATS2019Symposium.pdf}{\textbf{Kats, D.J.}, Adie, Y., Tlimat, A., Tarabichi, Y. Providers at an Academic Safety-Net Hospital System Tend to Refer Patients for Lung Cancer Screening Based on Patient Risk, but Demographic Disparities Persist. American Thoracic Society International Conference; Dallas, TX. 2019.}

		\item\label{lepow17}[Local] \textbf{Kats, D.J.}, Tarabichi, Y., Kaelber, D.C., Thornton, J.D. The Impact of Smoking History EHR Fluctuations on Lung Cancer Screening Practices. Lepow Day; Cleveland, OH. 2017.

	\end{enumerate}

\bibsec{Poster Presentations}
	\begin{enumerate}[resume]

		\item\label{ats20tlimat}[International] \href{https://www.atsjournals.org/doi/pdf/10.1164/ajrccm-conference.2020.201.1_MeetingAbstracts.A5933}{Tlimat, A., O. Adeoye, \textbf{Kats, D.J.}, Tarabichi, Y. Could Patients at a Safety-Net Healthcare Systems Be Too Sick to Be Screened for Lung Cancer? American Thoracic Society International Conference; Philadelphia, PA. 2020.}

		\item\label{ats19poster}[International] \href{https://www.dankats.com/research/ATS2019Poster.pdf}{\textbf{Kats, D.J.}, Tlimat, A., Adie, Y., Tarabichi, Y. Can Historical Electronic Health Record Smoking Data Be Leveraged to Improve the Selection of Patients for Lung Cancer Screening? American Thoracic Society International Conference; Dallas, TX. 2019.}

		\item\label{ats19adie}[International] \href{https://doi.org/10.1164/ajrccm-conference.2019.199.1_MeetingAbstracts.A7287}{Adie, Y., Tlimat, A., \textbf{Kats, D.J.}, Perzynski, A., Tarabichi, Y. Neighborhood Disadvantage and Lung Cancer Incidence in an Electronic Health Record Cohort. American Thoracic Society International Conference; Dallas, TX. 2019.}

		\item\label{ats19tlimat}[International] \href{https://doi.org/10.1164/ajrccm-conference.2019.199.1_MeetingAbstracts.A6712}{Tlimat, A., \textbf{Kats, D.J.}, Perzynski, A., Tarabichi, Y. A Temporal Analysis of Variation in Smoking Intensity in the Cleveland Area by Strata of Neighborhood Socioeconomic Deprivation. American Thoracic Society International Conference; Dallas, TX. 2019.}

		\item\label{ats18}[International] \href{http://www.dankats.com/research/ATS2018.pdf}{\textbf{Kats, D.J.}, Thornton, J.D., Kaelber, D.C., Tarabichi, Y. Structured Smoking Exposure Variability in the Electronic Health Record Hurts Lung Cancer Screening Practices. American Thoracic Society International Conference; San Diego, CA. 2018.}

		\item\label{scifest15}[Local] \href{https://kb.brandeis.edu/display/SCI/SciFest+V+Abstracts?preview=/16613394/16613408/scifest-2015-abstracts.pdf}{\textbf{Kats, D.J.}, Gollapalli, D., Dang, Y., Hedstrom, L. Moonlighting Interactions of IMPDH Affect \textit{Escherichia~coli} Growth. SciFest V; Waltham, MA. 2015. (Poster \#2015.421)}

		\item\label{scifest14}[Local] \href{https://kb.brandeis.edu/download/attachments/7996171/scifest-2014.pdf?version=1&modificationDate=1423410173000&api=v2}{\textbf{Kats, D.J.}, Gollapalli, D., Dang, Y., Hedstrom, L. Moonlighting Interactions of \textit{Escherichia~coli} IMPDH. SciFest IV; Waltham, MA. 2014. (Poster \#2014.311)}
	
	\end{enumerate}

\bibsec{Non-Peer-Reviewed}

	\begin{enumerate}[resume]

		\item\label{rainbow-sti} \textbf{Kats, D.J.}, Lie, S. Sexually Transmitted Infections. Massachusetts General Hospital \textit{for} Children Resource Book Pediatric Housestaff Manual. 2021.

		\item\label{rainbow-ekg} \textbf{Kats, D.J.} EKG Basics. Massachusetts General Hospital \textit{for} Children Resource Book Pediatric Housestaff Manual. 2021.

		\item\label{rainbow-bradycardia} \textbf{Kats, D.J.} Arrhythmias: Bradycardia. Massachusetts General Hospital \textit{for} Children Resource Book Pediatric Housestaff Manual. 2021.

		\item\label{rainbow-wpw} \textbf{Kats, D.J.} Arrhythmias: Wolff-Parkinson White. Massachusetts General Hospital \textit{for} Children Resource Book Pediatric Housestaff Manual. 2021.

		\item\label{rainbow-kawasaki} \textbf{Kats, D.J.} Cardiac Infection and Inflammation: Kawasaki Disease. Massachusetts General Hospital \textit{for} Children Resource Book Pediatric Housestaff Manual. 2021.

		\item\label{rainbow-constipation} \textbf{Kats, D.J.}, Olshan, K. Constipation. Massachusetts General Hospital \textit{for} Children Resource Book Pediatric Housestaff Manual. 2021.

		\item\label{rainbow-nausea} Diacovo, N., \textbf{Kats, D.J.} Nausea. Massachusetts General Hospital \textit{for} Children Resource Book Pediatric Housestaff Manual. 2021.

		\item\label{rainbow-covid19} \textbf{Kats, D.J.} COVID-19. Massachusetts General Hospital \textit{for} Children Resource Book Pediatric Housestaff Manual. 2021.

		\item\label{rainbow-misc} \textbf{Kats, D.J.} Multisystem Inflammatory Syndrome in Children. Massachusetts General Hospital \textit{for} Children Resource Book Pediatric Housestaff Manual. 2021.

		\item\label{rainbow-mdro} \textbf{Kats, D.J.} Multi-Drug Resistant Organisms. Massachusetts General Hospital \textit{for} Children Resource Book Pediatric Housestaff Manual. 2021.

		\item\label{rainbow-common-infections} \textbf{Kats, D.J.} Table of Common Infections. Massachusetts General Hospital \textit{for} Children Resource Book Pediatric Housestaff Manual. 2021.

		\item\label{rainbow-ams} \textbf{Kats, D.J.} Altered Mental Status. Massachusetts General Hospital \textit{for} Children Resource Book Pediatric Housestaff Manual. 2021.

		\item\label{rainbow-newborn-exam} \textbf{Kats, D.J.} Examination of the Newborn. Massachusetts General Hospital \textit{for} Children Resource Book Pediatric Housestaff Manual. 2021.

		\item\label{rainbow-newborn-exam} \textbf{Kats, D.J.} Hyperbilirubinemia of the Newborn. Massachusetts General Hospital \textit{for} Children Resource Book Pediatric Housestaff Manual. 2021.

		\item\label{rainbow-newborn-exam} \textbf{Kats, D.J.} Pain Management: Opioids. Massachusetts General Hospital \textit{for} Children Resource Book Pediatric Housestaff Manual. 2021.

		\item\label{rainbow-newborn-exam} \textbf{Kats, D.J.} Other Symptom Management: Nausea, Constipation, Dyspnea. Massachusetts General Hospital \textit{for} Children Resource Book Pediatric Housestaff Manual. 2021.

		\item\label{mdthesis} \textbf{Kats, D.J.} Lung cancer risk stratification, Down syndrome, and epileptic spasms: A journey through informatics, healthcare disparities, and quality improvement [MD thesis]. Cleveland, OH: Case Western Reserve University School of Medicine. 2020.

		\item\label{bsthesis} \href{http://hdl.handle.net/10192/32359}{\textbf{Kats, D.J.} Inosine 5'-monophosphate dehydrogenase: A collection of mysterious binding sites and regulation [BS honors thesis]. Waltham, MA: Brandeis University. 2016.}

	\end{enumerate}

\end{adjustwidth}

%------------------------------------------------

\mysec{Institutional Service}
\begin{adjustwidth}{\blockindent}{0cm}

\job{Housestaff Quality \& Patient Safety Committee}{Massachusetts General Hospital}{Pediatrics Representative}{August 2021 -- Present}
\begin{itemize}
	\item Nominated by the Pediatrics Program Director, Quality Chair, and Chief Residents
\end{itemize}

\job{Wards Redesign Process Improvement}{Massachusetts General Hospital \emph{for} Children}{PGY-1 Representative}{March -- August 2021}
\begin{itemize}
	\item Represented the PGY-1 residents' interests during the Wards Redesign improvement project together with Nursing, PT, OT, SLP, Pharmacy, and Case Management.
	\item Member of the Rounds and Communication working groups.
\end{itemize}

\job{Advocacy Committee}{Massachusetts General Hospital \emph{for} Children}{Member}{November 2020 -- June 2021}
\begin{itemize}
	\item Organized residency-wide advocacy events, culminating in \href{https://rfdash.weebly.com/}{Residents and Fellows Day at the State House}
\end{itemize}

\jobtitle{\textbf{Interpreter Accessibility}, Massachusetts General Hospital}{November 2020 -- Present}
\begin{itemize}
	\item Worked with Interpreter Services, the Chief Medical Information Officer, and the Director of Health Information Services to make interpreters easier to access for patient-facing clinicians
	\item Created a QR code-based way to bypass the phone tree to expedite acquiring interpreters for patients (\href{https://www.katsmd.com/ipop}{www.katsmd.com/ipop})
\end{itemize}

\job{Advocacy Cause of the Month}{Massachusetts General Hospital \emph{for} Children}{Organizer}{November -- Febuary 2020}
\begin{itemize}
	\item Planned the ``Reproductive Health and Teen Pregnancy'' Cause of the Month
	\item Organized a noon conference: ``The History, Current Status, \& Future Directions of Family Planning/Abortion Laws in Massachusetts'' by Jen Childs-Roshak, MD, MBA
\end{itemize}

\job{Student Committee on Admissions}{Case Western Reserve University School of Medicine}{Co-Chair}{January 2017 -- January 2018}
\begin{itemize}
	\item Coordinated admissions interviews, tours, and lunches
	\item Attended Admissions Committee Meetings as a non-voting participant
\end{itemize}
\newpage

\job{Peer Handoff}{Case Western Reserve University School of Medicine}{Volunteer}{July 2017}
\begin{itemize}
	\item Led small and large group sessions during new student orientation
\end{itemize}

\job{Diversity Planning Committee}{Case Western Reserve University School of Medicine}{Member}{June -- July 2017}
\begin{itemize}
	\item Helped plan diversity training for new student orientation
\end{itemize}

\end{adjustwidth}

%------------------------------------------------

\mysec{Leadership and Community Service}
\begin{adjustwidth}{\blockindent}{0cm}

\job{\href{https://www.bincabps.org/}{Boston International Newcomers Academy}}{Boston, MA}{Volunteer}{May 2021}
\begin{itemize}
	\item {[Lecture]} Human papillomavirus infection: disease and vaccine (see \textsc{bibliography} \#\ref{binca-hpv})
\end{itemize}

\job{\href{http://www.prisonbookprogram.org}{Prison Book Program}}{Quincy, MA}{Volunteer}{October 2019}
\begin{itemize}
	\item Selected and packaged books for prisoners around the U.S., according to their requests
\end{itemize}

\job{\href{http://www.swcpc.org}{Southwest Corridor Park Conservancy}}{Boston, MA}{Volunteer}{October 2019}
\begin{itemize}
	\item Cleaned Claremont Park
\end{itemize}

\job{\href{http://www.youthbuildboston.org/}{Youth Build Boston}}{Roxbury, MA}{Volunteer}{April 2019}
\begin{itemize}
	\item Tutored out-of-school youth studying for a high school equivalency exam
\end{itemize}

\job{\href{http://www.redcross.org/local/massachusetts}{American Red Cross of Eastern Massachusetts Food Pantry}}{Boston, MA}{Volunteer}{December 2018}
\vspace{12pt}

\job{\href{http://www.x-celeducation.org/}{X-Cel Education}}{Dorchester, MA}{Volunteer}{December 2018}
\begin{itemize}
	\item Tutored math to adults studying for a high school equivalency exam
\end{itemize}

\job{Greater Boston Food Bank}{Boston, MA}{Volunteer}{December 2018}
\vspace{12pt}

\job{\href{https://www.techgoeshome.org/}{Tech Goes Home}}{Dorchester and Roxbury, MA}{Volunteer}{December 2018 -- January 2019}
\begin{itemize}
	\item Assisted adults learning fundamental computer skills
\end{itemize}

\job{Fairfax Four Corner Program}{Cuyahoga County Juvenile Detention Center}{Coordinator}{September 2018 -- October 2018}
\begin{itemize}

	\item Helped develop a community service program in which medical students run weekly lessons for children in the Juvenile Detention Center as a formal class through the Cleveland Metropolitan School District

	\item Based on Maslow's Hierarchy of Needs, the curriculum first guides students through understanding how they entered the juvenile justice system; then, how they can examine and modify their behaviors to prevent future negative encounters with the justice system

\end{itemize}

\job{Sex Education}{Cuyahoga County Juvenile Detention Center}{Volunteer}{October 2017 -- February 2018}
\begin{itemize}

	\item Taught a three-day sex education curriculum to children in a juvenile detention center

	\item Topics covered: reproductive anatomy, hygiene, sexually transmitted infections, contraception, consent, and healthy relationships

\end{itemize}

\job{Anatomy Camp}{Case Western Reserve University School of Medicine}{Volunteer}{October -- November 2017}
\begin{itemize}

	\item Taught Cleveland middle and high school students general principles of biology related to the healthcare field

\end{itemize}

\job{Student Run Health Clinic}{Case Western Reserve University School of Medicine}{Volunteer}{June 2017 -- February 2018}
\begin{itemize}

	\item Junior Clinician: worked with a fourth year medical student to perform the initial history and physical on patients, followed by presenting to the attending

	\item Case Manager: worked with a social work student to assess patients' social needs prior to handing off to the Junior and Senior Clinicians

	\item Front Desk: registered patients for appointments

\end{itemize}

\job{Doc Opera (Fundraiser)}{Case Western Reserve University School of Medicine}{Dancer (1 performance)}{August -- December 2017}
\jobtitle{Dancer (3 performances)}{August -- December 2016}
\begin{itemize}

	\item Doc Opera is a fundraiser for the Student Run Health Clinic and consists of dances and skits entirely performed by medical students

	\item Danced in three performances during 2016: cha-cha, Bollywood fusion, and hip-hop

	\item Danced in one performance during 2017: fusion dance consisting of Bhangra, Bharatanatyam, and Kathak

\end{itemize}

\job{Sex Education}{American Medical Women's Association}{Volunteer}{November 2016 -- December 2017}
\begin{itemize}

	\item Taught a three-day sex education curriculum to underserved Cleveland middle school students

	\item Topics covered: reproductive anatomy, sexually transmitted infections, contraception, and consent

	\item Helped incorporate education on consent into the curriculum

\end{itemize}

\job{\href{http://www.brandeis.edu/walthamgroup/programs/spectrum.html}{SPECTRUM}{\normalfont ,} \href{http://www.brandeis.edu/walthamgroup/index.html}{Waltham Group}}{Brandeis University, Waltham, MA}{Coordinator}{November 2014 -- May 2016}
\jobtitle{Volunteer}{September 2012 -- November 2014}
\begin{itemize}

	\item Ran weekly tutoring, mentoring, and playgroup (with parent social group) programs

	\item Received \href{https://www.facebook.com/WSEPAC/home}{Waltham Special Education Parent Advisory Council}'s Rising Star (2015) and Kelly Beaumont-Mazzarini Inclusion (2016) awards

	\item Received \href{http://www.gwarc.org/}{Greater Waltham Arc}'s \href{http://www.gwarc.org/newsdetail/annual-meeting-2015/}{``Rags'' LaCava Community Service Award (2015)}

	\item Planned and hosted annual educational events about developmental disabilities

	\item Managed nonprofit budget (over \$6,000)

	\item Grew volunteer base from thirty to sixty members

\end{itemize}

\end{adjustwidth}

%------------------------------------------------

\mysec{Skills}

\begin{itemize}

	\item Programming in R, Python, Java, and MATLAB

	\item Basic web development: HTML, CSS, and JavaScript

	\item Document typesetting: \LaTeX

\end{itemize}

%------------------------------------------------

\mysec{Languages}

	\begin{itemize}

		\item Russian: fluent (certified as Qualified Bilingual Staff at MGH)

		\item Spanish: can moderately understand, but speech is limited

		\item American Sign Language: brief exposure, very limited vocabulary

	\end{itemize}

%------------------------------------------------

\vspace{-3pt}
\mysec{Interests}
\begin{adjustwidth}{\blockindent}{0cm}

	Bollywood films and dance, ballroom dancing, computer programming, baseball, cycling, hiking, skiing, and writing (\href{http://www.dankats.com/thoughts}{www.dankats.com/thoughts})

\end{adjustwidth}

\end{document}